Paper Analysis

### 2025-01-20 Paper_WriteUp/Paper_Plots.qmd
tidy up all the plots before section 5

```{r figure 1}
player_cohort_1 <- "sandro2502"

@@

```{r figure 3 - plot global parameters for 17-19}
data_path <- here("results/lichess1700-1900")

@@

# color_scheme_set("blue")

## easiest way to make this grayscale would be to not use mcmc_hist at all

@@

global_17_19_bullet_prev

ggsave(plot = global_17_19_bullet_prev, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "17_19_prev_global.png")), dpi = 600,
       height = 5, width = 7)

@@

```{r player level parameters for 17-19}
player_id <- as_tibble(bullet_17_19) |> 
  mutate(id = row_number()) |> 
  rename(player_name = value)

@@

## see how many contain 0
player_pars |> 
  group_by(player_name, param) |> 
  filter(param == 2) |> 
  summarise(lower = quantile(value, prob = 0.025),
            upper = quantile(value, prob = 0.975)) |> 
  mutate(contain_zero = ifelse(upper > 0 & lower < 0,
                         1, 0)) |> 
  filter(contain_zero == 0)

@@

ggsave(plot = winner_plot_17_19, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "17_19_prev_winner.png")), dpi = 600,
       height = 7, width = 7)

indiv_plot_17_19 <- player_pars |> 
  filter(param == 1) |> 
  ggplot(aes(y = reorder(player_name, value, FUN = median), x = value)) +
  stat_histinterval() +
  labs(x = "Estimated Player Effect", y = element_blank()) +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  theme_single_y()

@@

```{r figure 3 - global parameters for gm data}
data_path <- here("results/lichessGrandmasters")

fit_gm_bullet_prev <- 
  readRDS(file =paste0(data_path,"/all_rated_bullet_model_prev.RDS"))

@@

global_gm_bullet_prev

ggsave(plot = global_gm_bullet_prev, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "gm_prev_global.png")), dpi = 600,
       height = 5, width = 7)
```

```{r interpret the estimated coefficients gm}
#| eval: false
gamma_ests_gm <- fit_gm_bullet_prev$summary(variables = c("gamma1",
                                                          "gamma2")) |> 
  pull(mean)
## compute change in win probability for gamma1
1/(1 + exp(-1 * (0)))
1/(1 + exp(-1 * (gamma_ests_gm[1])))

## change in win probability for elo difference
1/(1 + exp(-1 * (0))) ## equally rated, playing as black
1/(1 + exp(-1 * (100 * gamma_ests_gm[2])))

@@

ggsave(plot = winner_plot_gm, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "gm_prev_winner.png")), dpi = 600,
       height = 7, width = 7)

## then repeat for player effects
indiv_plot_gm <- player_pars |> 
  filter(param == 1) |> 
  ggplot(aes(y = reorder(player_name, value, FUN = median), x = value)) +
  stat_histinterval() +
  labs(x = "Estimated Player Effect", y = element_blank(), 
       title = "GM Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  theme_single_y()

@@

```{r figure 5 - compare global params n-1 vs n-10}
## global effects first
data_path <- here("results/lichessGrandmasters")
fit_gm_bullet_10 <- 
  readRDS(file =paste0(data_path,"/all_rated_bullet_model.RDS"))

@@

ggsave(plot = hist_comp_global, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "gm_comp_global.png")), dpi = 600,
       height = 3.5, width = 7)

@@

hist_comp_winner <- player_pars_pre |> 
  filter(param == 2) |> 
  mutate(y = reorder(player_name, value, FUN = median)) |> 
  bind_rows(player_pars_pre_10 |> filter(param == 2) |> 
              mutate(y = as.factor(player_name))) |> 
  ggplot(aes(x = value, y = y,
             color = model)) +
  stat_pointinterval(position = position_dodge(width = 1)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_single_y() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 2)) +
  scale_color_viridis_d(option = "D")

@@

## then player effects
## should update this also
hist_comp_player <- player_pars_pre |> 
  filter(param == 1) |> 
  mutate(y = reorder(player_name, value, FUN = median)) |> 
  bind_rows(player_pars_pre_10 |> filter(param == 1) |> 
              mutate(y = as.factor(player_name))) |> 
  ggplot(aes(x = value, y = y,
             color = model)) +
  stat_pointinterval(position = position_dodge(width = 1)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_single_y() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 2)) +
  scale_color_viridis_d(option = "D")

@@

## TO DO - not a current paper plot, not updated
data_path <- here("results/lichess1700-1900")
fit_17_19_bullet_prev <- readRDS(file = paste0(data_path,
                                              "/all_rated_bullet_model_prev.RDS"))
bullet_17_19 <- readRDS(file = paste0(data_path, "/users_bullet.RDS"))
fit_17_19_blitz_prev <- readRDS(file = paste0(data_path,
                                              "/all_rated_blitz_model_prev.RDS"))
blitz_17_19 <- readRDS(file = paste0(data_path, "/users_blitz.RDS"))

## compare global effects first
bullet_pars <- fit_17_19_bullet_prev$draws(c("mu_beta",
                                                          "gamma1", "gamma2",
                           "sigma_1", "tau[1]", "tau[2]",
                           "sigma_g1", "sigma_g2")) |> 
  as_draws_df() |> 
  pivot_longer(cols = "mu_beta":"sigma_g2") |> 
  mutate(model = "Bullet")

blitz_pars <- fit_17_19_blitz_prev$draws(c("mu_beta",
                                                          "gamma1", "gamma2",
                           "sigma_1", "tau[1]", "tau[2]",
                           "sigma_g1", "sigma_g2")) |> 
  as_draws_df() |> 
  pivot_longer(cols = "mu_beta":"sigma_g2") |> 
  mutate(model = "Blitz")

bul_blit_comp_global <- bind_rows(bullet_pars, blitz_pars) |> 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_grid(rows = vars(model), cols = vars(name), scales = "free",
              labeller = labeller(name = facet_labels)) +
  theme_8col() +
  labs(x = element_blank(), y = element_blank()) +
  scale_x_continuous(breaks = breaks_pretty(n = 2))

@@

## then repeat for winner and player effects
player_pars_bullet <- fit_17_19_bullet_prev$draws() |> 
  as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id") |> 
  mutate(model = "Bullet")

player_pars_blitz <- fit_17_19_blitz_prev$draws() |> 
  as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id") |> 
  mutate(model = "Blitz")

comp_17_19_winner <- bind_rows(player_pars_bullet, player_pars_blitz) |> 
  filter(id < 7) |> 
  filter(param == 2) |> 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_grid(rows = vars(model), cols = vars(player_name), scales = "free") +
  theme_6col() +
  labs(x = element_blank(), y = element_blank()) +
  scale_x_continuous(breaks = breaks_pretty(n = 3))

@@

comp_17_19_player <- bind_rows(player_pars_bullet, player_pars_blitz) |> 
  filter(id < 7) |> 
  filter(param == 1) |> 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_grid(rows = vars(model), cols = vars(player_name), scales = "free") +
  theme_6col() +
  labs(x = element_blank(), y = element_blank()) +
  scale_x_continuous(breaks = breaks_pretty(n = 3))

@@

```{r figure 5 - bullet v blitz gm}
data_path <- here("results/lichessGrandmasters")

fit_gm_bullet_prev <- readRDS(file = paste0(data_path,
                                              "/all_rated_bullet_model_prev.RDS"))
bullet_gm <- readRDS(file = paste0(data_path, "/users_bullet.RDS"))
fit_gm_blitz_prev <- readRDS(file = paste0(data_path,
                                              "/all_rated_blitz_model_prev.RDS"))
blitz_gm <- readRDS(file = paste0(data_path, "/users_blitz.RDS"))
## compare global effects first
bullet_pars <- fit_gm_bullet_prev$draws(c("mu_beta",
                                          "gamma1", "gamma2")) |> 
  as_draws_df() |> 
  pivot_longer(cols = "mu_beta":"gamma2") |> 
  mutate(model = "Bullet")

blitz_pars <- fit_gm_blitz_prev$draws(c("mu_beta",
                                        "gamma1", "gamma2")) |> 
  as_draws_df() |> 
  pivot_longer(cols = "mu_beta":"gamma2") |> 
  mutate(model = "Blitz")

bul_blit_gm_comp_global <- bind_rows(bullet_pars, blitz_pars) |> 
  ggplot(aes(x = value, y = name, color = model)) +
  stat_pointinterval(position = position_dodge(width = 0.2)) +
  facet_wrap(~name,
             scales = "free",
             labeller = labeller(name = facet_labels)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_3col() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 2)) +
  scale_color_viridis_d(option = "H")

@@

ggsave(plot = bul_blit_gm_comp_global, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "bul_blitz_comp_gm_global.png")), dpi = 600,
       height = 3.5, width = 7)

## then repeat for winner and player effects
player_pars_bullet <- fit_gm_bullet_prev$draws() |> 
  as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id") |> 
  mutate(model = "Bullet")

@@

comp_gm_winner <- player_pars_bullet |> 
  filter(param == 2) |> 
  mutate(y = reorder(player_name, value, FUN = median)) |> 
  bind_rows(player_pars_blitz |> 
              filter(param == 2) |> 
              mutate(y = as.factor(player_name))) |> 
  ggplot(aes(x = value, y = y,
             color = model)) +
  stat_pointinterval(position = position_dodge(width = 1)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_single_y() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 3)) +
  scale_color_viridis_d(option = "H")

comp_gm_winner

ggsave(plot = comp_gm_winner, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "bul_blitz_comp_gm_winner.png")), dpi = 600,
       height = 5, width = 7)
```

## TO DO - this needs to be updated
comp_gm_player <- bind_rows(player_pars_bullet, player_pars_blitz) |> 
  filter(id < 7) |> 
  filter(param == 1) |> 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_grid(rows = vars(model), cols = vars(player_name), scales = "free") +
  theme_6col() +
  labs(x = element_blank(), y = element_blank()) +
  scale_x_continuous(breaks = breaks_pretty(n = 3))

@@

<!-- TO DO - Update Below here -->
<!-- Everything down as far as here up to date. -->
<!-- setting everything below to eval: false for now -->

@@

>>>>

```{r figure 1}
## Sydney's code for this figure

player_cohort_1 <- "sandro2502"

@@

```{r figure 3 left - plot global parameters for 17-19}
data_path <- here("results/lichess1700-1900")

@@

@@

global_17_19_bullet_prev
ggsave(plot = global_17_19_bullet_prev, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "17_19_prev_global.png")), dpi = 600,
       height = 5, width = 7)
```

@@

```{r player level parameters for 17-19}
#| eval: false

player_id <- as_tibble(bullet_17_19) |> 
  mutate(id = row_number()) |> 
  rename(player_name = value)

@@

## see how many contain 0
player_pars |> 
  group_by(player_name, param) |> 
  filter(param == 2) |> 
  summarise(lower = quantile(value, prob = 0.025),
            upper = quantile(value, prob = 0.975)) |> 
  mutate(contain_zero = ifelse(upper > 0 & lower < 0,
                         1, 0)) |> 
  filter(contain_zero == 0)
```

@@

ggsave(plot = winner_plot_17_19, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "17_19_prev_winner.png")), dpi = 600,
       height = 7, width = 7)
```

```{r plot player effects}
#| eval: false
indiv_plot_17_19 <- player_pars |> 
  filter(param == 1) |> 
  ggplot(aes(y = reorder(player_name, value, FUN = median), x = value)) +
  stat_histinterval() +
  labs(x = "Estimated Player Effect", y = element_blank()) +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  theme_single_y()

@@

```{r figure 3 right - global parameters for gm data}
data_path <- here("results/lichessGrandmasters")

fit_gm_bullet_prev <- 
  readRDS(file = paste0(data_path,"/all_rated_bullet_model_prev.RDS"))

@@

global_gm_bullet_prev
ggsave(plot = global_gm_bullet_prev, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "gm_prev_global.png")), dpi = 600,
       height = 5, width = 7)
```

```{r interpret the estimated coefficients gm}
#| eval: false
gamma_ests_gm <- fit_gm_bullet_prev$summary(variables = c("gamma1",
                                                          "gamma2")) |> 
  pull(mean)
## compute change in win probability for gamma1
1/(1 + exp(-1 * (0)))
1/(1 + exp(-1 * (gamma_ests_gm[1])))
## change in win probability for elo difference
1/(1 + exp(-1 * (0))) ## equally rated, playing as black
1/(1 + exp(-1 * (100 * gamma_ests_gm[2])))
```

@@

ggsave(plot = winner_plot_gm, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "gm_prev_winner.png")), dpi = 600,
       height = 7, width = 7)
```

```{r plot player effects}
#| eval: false
## then repeat for player effects
indiv_plot_gm <- player_pars |> 
  filter(param == 1) |> 
  ggplot(aes(y = reorder(player_name, value, FUN = median), x = value)) +
  stat_histinterval() +
  labs(x = "Estimated Player Effect", y = element_blank(), 
       title = "GM Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  theme_single_y()

@@

```{r figure 5 left - compare global params n-1 vs n-10}
## global effects first
data_path <- here("results/lichessGrandmasters")
fit_gm_bullet_10 <- 
  readRDS(file =paste0(data_path,"/all_rated_bullet_model.RDS"))

@@

ggsave(plot = hist_comp_global, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "gm_comp_global.png")), dpi = 600,
       height = 3.5, width = 7)
```

@@

hist_comp_winner <- player_pars_pre |> 
  filter(param == 2) |> 
  mutate(y = reorder(player_name, value, FUN = median)) |> 
  bind_rows(player_pars_pre_10 |> filter(param == 2) |> 
              mutate(y = as.factor(player_name))) |> 
  ggplot(aes(x = value, y = y,
             color = model)) +
  stat_pointinterval(position = ggstance::position_dodgev(height = 0.5)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_single_y() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 2)) +
  scale_color_viridis_d(option = "D")

@@

## then player effects
## should update this also
hist_comp_player <- player_pars_pre |> 
  filter(param == 1) |> 
  mutate(y = reorder(player_name, value, FUN = median)) |> 
  bind_rows(player_pars_pre_10 |> filter(param == 1) |> 
              mutate(y = as.factor(player_name))) |> 
  ggplot(aes(x = value, y = y,
             color = model)) +
  stat_pointinterval(position = ggstance::position_dodgev(height = 0.5)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_single_y() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 2)) +
  scale_color_viridis_d(option = "D")

@@

## Potential Supplement Plots
data_path <- here("results/lichess1700-1900")
fit_17_19_bullet_prev <- readRDS(file = paste0(
  data_path,
  "/all_rated_bullet_model_prev.RDS"
))
bullet_17_19 <- readRDS(file = paste0(data_path, "/users_bullet.RDS"))
fit_17_19_blitz_prev <- readRDS(file = paste0(
  data_path,
  "/all_rated_blitz_model_prev.RDS"
))
blitz_17_19 <- readRDS(file = paste0(data_path, "/users_blitz.RDS"))

player_id_17_19 <- as_tibble(bullet_17_19) |> 
  mutate(id = row_number()) |> 
  rename(player_name = value)

## compare global effects first
bullet_pars <- fit_17_19_bullet_prev$draws(c(
  "mu_beta",
  "gamma1", "gamma2"
)) |>
  as_draws_df() |>
  pivot_longer(cols = "mu_beta":"gamma2") |>
  mutate(model = "Bullet")

blitz_pars <- fit_17_19_blitz_prev$draws(c(
  "mu_beta",
  "gamma1", "gamma2"
)) |>
  as_draws_df() |>
  pivot_longer(cols = "mu_beta":"gamma2") |>
  mutate(model = "Blitz")

bul_blit_comp_global <- bind_rows(bullet_pars, blitz_pars) |>
  ggplot(aes(value, color = model))  +
  stat_pointinterval(position = position_dodge(width = 0.2)) +
  facet_wrap(~name,
             scales = "free",
             labeller = labeller(name = facet_labels)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_3col() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 2)) +
  scale_color_viridis_d(option = "H")

@@

## then repeat for winner and player effects
player_pars_bullet <- fit_17_19_bullet_prev$draws() |> 
  as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id_17_19, by = "id") |> 
  mutate(model = "Bullet")

player_pars_blitz <- fit_17_19_blitz_prev$draws() |> 
  as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id_17_19, by = "id") |> 
  mutate(model = "Blitz")

## need to keep only players which are in both 
## bullet and blitz

common_players <- intersect(unique(player_pars_bullet$player_name),
                            unique(player_pars_blitz$player_name))

comp_17_19_winner <- player_pars_bullet |> 
  filter(param == 2) |> 
  filter(player_name %in% common_players) |> 
  mutate(y = reorder(player_name, value, FUN = median)) |> 
  bind_rows(player_pars_blitz |>
              filter(param == 2) |>
              filter(player_name %in% common_players) |>
              mutate(y = as.factor(player_name))) |>
  ggplot(aes(x = value, y = y,
             color = model)) +
  stat_pointinterval(position = ggstance::position_dodgev(height = 0.5)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_single_y() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 2)) +
  scale_color_viridis_d(option = "D")

@@

comp_17_19_player <- player_pars_bullet |> 
  filter(param == 1) |> 
  filter(player_name %in% common_players) |> 
  mutate(y = reorder(player_name, value, FUN = median)) |> 
  bind_rows(player_pars_blitz |>
              filter(param == 1) |>
              filter(player_name %in% common_players) |>
              mutate(y = as.factor(player_name))) |>
  ggplot(aes(x = value, y = y,
             color = model)) +
  stat_pointinterval(position = ggstance::position_dodgev(height = 0.5)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_single_y() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 2)) +
  scale_color_viridis_d(option = "D")

@@

```{r figure 5 right - bullet v blitz gm}
data_path <- here("results/lichessGrandmasters")
fit_gm_bullet_prev <- readRDS(file = paste0(
  data_path,
  "/all_rated_bullet_model_prev.RDS"
))
bullet_gm <- readRDS(file = paste0(data_path, "/users_bullet.RDS"))
fit_gm_blitz_prev <- readRDS(file = paste0(
  data_path,
  "/all_rated_blitz_model_prev.RDS"
))
blitz_gm <- readRDS(file = paste0(data_path, "/users_blitz.RDS"))
## compare global effects first
bullet_pars <- fit_gm_bullet_prev$draws(c(
  "mu_beta",
  "gamma1", "gamma2"
)) |>
  as_draws_df() |>
  pivot_longer(cols = "mu_beta":"gamma2") |>
  mutate(model = "Bullet")

blitz_pars <- fit_gm_blitz_prev$draws(c(
  "mu_beta",
  "gamma1", "gamma2"
)) |>
  as_draws_df() |>
  pivot_longer(cols = "mu_beta":"gamma2") |>
  mutate(model = "Blitz")

bul_blit_gm_comp_global <- bind_rows(bullet_pars, blitz_pars) |>
  ggplot(aes(x = value, y = name, color = model)) +
  stat_pointinterval(position = ggstance::position_dodgev(height = 0.5)) +
  facet_wrap(~name,
    scales = "free",
    labeller = labeller(name = facet_labels)
  ) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_3col() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 2)) +
  scale_color_viridis_d(option = "H")

@@

ggsave(
  plot = bul_blit_gm_comp_global,
  filename = paste0(here(
    "Paper_WriteUp", "paper_figures",
    "bul_blitz_comp_gm_global.png"
  )), dpi = 600,
  height = 3.5, width = 7
)
```

```{r figure 6 - comparison between bullet and blitz winner}
## then repeat for winner and player effects
player_id <- as_tibble(bullet_gm) |> 
  mutate(id = row_number()) |> 
  rename(player_name = value)

player_pars_bullet <- fit_gm_bullet_prev$draws() |> 
  as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id") |> 
  mutate(model = "Bullet")

@@

comp_gm_winner <- player_pars_bullet |> 
  filter(param == 2) |> 
  mutate(y = reorder(player_name, value, FUN = median)) |> 
  bind_rows(player_pars_blitz |> 
              filter(param == 2) |> 
              mutate(y = as.factor(player_name))) |> 
  ggplot(aes(x = value, y = y,
             color = model)) +
  stat_pointinterval(position = ggstance::position_dodgev(height = 0.5)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_single_y() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 3)) +
  scale_color_viridis_d(option = "H")

comp_gm_winner
ggsave(plot = comp_gm_winner, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "bul_blitz_comp_gm_winner.png")), dpi = 600,
       height = 5, width = 7)
```

```{r}
#| eval: false
## player effects also
comp_gm_player <- player_pars_bullet |> 
  filter(param == 1) |> 
  mutate(y = reorder(player_name, value, FUN = median)) |> 
  bind_rows(player_pars_blitz |> 
              filter(param == 1) |> 
              mutate(y = as.factor(player_name))) |> 
  ggplot(aes(x = value, y = y,
             color = model)) +
  stat_pointinterval(position = ggstance::position_dodgev(height = 0.5)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_single_y() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 3)) +
  scale_color_viridis_d(option = "H")

@@

<!-- TO DO - Update Below here -->
<!-- Everything down as far as here up to date. -->
<!-- setting everything below to eval: false for now -->
<!-- Updating everything below here -->

@@

## Fitting the Model with n=5 as History
